Parareal Algorithm

### 2014-12-06 paper.tex
added algorithm, removed bunch of stuff

\begin{document}
\title{Parareal Algorithm}
\author{Wesley Chen, Brandon Sim, Andy Shi \\
Harvard University, Applied Math 205 Final Project}
\date{December 15, 2014}
\maketitle

@@

% Put your stuff here

\section{Abstract}

We LIKE TO PLAY LEAGUE.

@@

\begin{algorithm}[t]
 \KwIn{Replication parameter $C$.}
 \KwIn{$P$ processors arranged into $C$ rows and $T=P/C$ teams.}
 \KwIn{Set $\mathcal{T}$ of $N$ particles and associated charges and results.}
 In parallel on all processors, $r = $ rank\;
 Scatter particles from master to team leaders, $\mathcal{T}_t$\;
 Broadcast $\mathcal{T}_t$ from team leader to team members\;
 Copy $\mathcal{T}_t$, the set of targets, to $\mathcal{S}_t$, the set of sources\;
 Given $c$th member of team $t$, shift $\mathcal{S}_t$ by $c$ along row\;
 \For{\normalfont{iteration} $i < 1$}{
   Compute symmetric interaction of $\mathcal{T}_t$ and $\mathcal{S}_t$\;
 }
 Reduce the results within a team\;
 Gather the results between team leaders\;
 \caption{Symmetric Diagonal $N$-body}
 \label{alg:symmdiag}
\end{algorithm}

>>>>

\begin{document}
\title{Parareal Algorithm}
\author{Wesley Chen, Brandon Sim, Andy Shi \\
Harvard University, Applied Math 205 Final Project}
\date{December 15, 2014}

@@

% Put your stuff here
\twocolumn[
    \begin{@twocolumnfalse}
    \maketitle
    \begin{abstract}

    Lorem ipsum dolor sit amet, consectetur adipiscing elit. Donec a diam
    lectus.  Sed sit amet ipsum mauris. Maecenas congue ligula ac quam viverra
    nec consectetur ante hendrerit. Donec et mollis dolor. Praesent et diam eget
    libero egestas mattis sit amet vitae augue. Nam tincidunt congue enim, ut
    porta lorem lacinia consectetur. Donec ut libero sed arcu vehicula ultricies
    a non tortor.  Lorem ipsum dolor sit amet, consectetur adipiscing elit.
    Aenean ut gravida lorem. Ut turpis felis, pulvinar a semper sed, adipiscing
    id dolor. Pellentesque auctor nisi id magna consequat sagittis. Curabitur
    dapibus enim sit amet elit pharetra tincidunt feugiat nisl imperdiet. Ut
    convallis libero in urna ultrices accumsan.  Donec sed odio eros. Donec
    viverra mi quis quam pulvinar at malesuada arcu rhoncus. Cum sociis natoque
    penatibus et magnis dis parturient montes, nascetur ridiculus mus. In rutrum
    accumsan ultricies. Mauris vitae nisi at sem facilisis semper ac in est.

    \end{abstract}
  \end{@twocolumnfalse}
]

@@

\begin{algorithm}[t]
    \KwIn{Temporal discretization $t^n = t_0 + n \Delta t, \, n = 1,2,\ldots,N$}
    \KwIn{Coarse scheme $g_{\Delta t}$}
    \KwIn{Finer scheme $g_{\textnormal{fine}}$}
    Compute $u_1^{n+1} = g_{\Delta t}(t^n, u^n)$\;
    Compute the corrections $\delta g^n(u_1^n) = g_{\textnormal{fine}}(t^n,
    u^n) - g_{\Delta t}(t^n, u^n)$ in parallel\;
    Add the prediction and correction terms as $u_2^{n+1} = g_{\Delta
    t}(t^n, u_2^n) + \delta g^n(u_1^n)$\;
    Repeat steps 2 and 3, incrementing the iteration label and using $u_{k+1}^0
    = u^0$ as the initial condition\
    }
 \caption{Parareal}
 \label{alg:parareal}
\end{algorithm}
